\documentclass[]{article}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifxetex
  \usepackage{fontspec,xltxtra,xunicode}
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\else
  \ifluatex
    \usepackage{fontspec}
    \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
    \newcommand{\euro}{€}
  \else
    \usepackage[utf8]{inputenc}
    \usepackage{eurosym}
  \fi
\fi
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex,
              colorlinks=true,
              linkcolor=blue]{hyperref}
\else
  \usepackage[unicode=true,
              colorlinks=true,
              linkcolor=blue]{hyperref}
\fi
\hypersetup{breaklinks=true, pdfborder={0 0 0}}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}


\usepackage{fancyvrb}
\usepackage{color}
\usepackage[UTF-8]{inputenc}



\makeatletter
\def\PY@reset{\let\PY@it=\relax \let\PY@bf=\relax%
    \let\PY@ul=\relax \let\PY@tc=\relax%
    \let\PY@bc=\relax \let\PY@ff=\relax}
\def\PY@tok#1{\csname PY@tok@#1\endcsname}
\def\PY@toks#1+{\ifx\relax#1\empty\else%
    \PY@tok{#1}\expandafter\PY@toks\fi}
\def\PY@do#1{\PY@bc{\PY@tc{\PY@ul{%
    \PY@it{\PY@bf{\PY@ff{#1}}}}}}}
\def\PY#1#2{\PY@reset\PY@toks#1+\relax+\PY@do{#2}}

\expandafter\def\csname PY@tok@gd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@gu\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.50,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@gt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.25,0.82}{##1}}}
\expandafter\def\csname PY@tok@gs\endcsname{\let\PY@bf=\textbf}
\expandafter\def\csname PY@tok@gr\endcsname{\def\PY@tc##1{\textcolor[rgb]{1.00,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@cm\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@vg\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@m\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@go\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.50,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@ge\endcsname{\let\PY@it=\textit}
\expandafter\def\csname PY@tok@vc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@il\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@cs\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@cp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.74,0.48,0.00}{##1}}}
\expandafter\def\csname PY@tok@gi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.63,0.00}{##1}}}
\expandafter\def\csname PY@tok@gh\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@ni\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.60,0.60,0.60}{##1}}}
\expandafter\def\csname PY@tok@nl\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.63,0.00}{##1}}}
\expandafter\def\csname PY@tok@nn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@no\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@na\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.49,0.56,0.16}{##1}}}
\expandafter\def\csname PY@tok@nb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@nc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@nd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\expandafter\def\csname PY@tok@ne\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.82,0.25,0.23}{##1}}}
\expandafter\def\csname PY@tok@nf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@si\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
\expandafter\def\csname PY@tok@s2\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@vi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@nt\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@nv\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@s1\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sx\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@bp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@c1\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@kc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@c\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@mf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@err\endcsname{\def\PY@bc##1{\setlength{\fboxsep}{0pt}\fcolorbox[rgb]{1.00,0.00,0.00}{1,1,1}{\strut ##1}}}
\expandafter\def\csname PY@tok@kd\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@ss\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@sr\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
\expandafter\def\csname PY@tok@mo\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@kn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@mi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@gp\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@o\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@kr\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@s\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@kp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@w\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.73,0.73}{##1}}}
\expandafter\def\csname PY@tok@kt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.69,0.00,0.25}{##1}}}
\expandafter\def\csname PY@tok@ow\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\expandafter\def\csname PY@tok@sb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@k\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@se\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.13}{##1}}}
\expandafter\def\csname PY@tok@sd\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}

\def\PYZbs{\char`\\}
\def\PYZus{\char`\_}
\def\PYZob{\char`\{}
\def\PYZcb{\char`\}}
\def\PYZca{\char`\^}
\def\PYZam{\char`\&}
\def\PYZlt{\char`\<}
\def\PYZgt{\char`\>}
\def\PYZsh{\char`\#}
\def\PYZpc{\char`\%}
\def\PYZdl{\char`\$}
\def\PYZti{\char`\~}


\def\PYZat{@}
\def\PYZlb{[}
\def\PYZrb{]}
\makeatother

\title{AV Assignment 2}
\author{Flavius Popescu, Jakub Hampl}
\date{}




\begin{document}
  
\maketitle
\abstract{Our assignment}

\section{Algorithms Used}

The bulk of our system relies on background subtraction and
thresholding. We have achieved very good performance using only very
simple techniques making more complicated techniques like model based
skin detection somewhat superfluous.

The first attempt was using the background image provided. However, we
soon realized that there were plenty of artifacts resulting fro subtle
differences between this image and the training set. We investigated the
use of normalized RGB, but many of the differences were probably more
due to haze, camera jitter and blur.

We found that taking an average image from all the possible data
provides a much better background image while also taking care of
removing most of the juggler from the image.

\subsection{Calculating the average background image}

To calculate the average background we iterate through all the images
and simply average their numerical values.

\begin{Verbatim}[commandchars=\\\{\}]\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{function}\PY{+w}{ }[avgbg] \PY{p}{=}\PY{+w}{ }\PY{n+nf}{avgall}\PY{p}{(}\PY{p}{)}
\PY{+w}{    }\PY{n}{files} \PY{p}{=} \PY{n}{dir}\PY{p}{(}\PY{l+s}{'}\PY{l+s}{juggle1/0*.jpg'}\PY{p}{)}\PY{p}{;}
    \PY{n}{avgbg} \PY{p}{=} \PY{n+nb}{zeros}\PY{p}{(}\PY{n+nb}{size}\PY{p}{(} \PY{n}{imread}\PY{p}{(}\PY{l+s}{'}\PY{l+s}{background.jpg'}\PY{p}{)}\PY{p}{)} \PY{p}{,} \PY{l+s}{'}\PY{l+s}{double'} \PY{p}{)}\PY{p}{;}
    \PY{k}{for} \PY{n}{ii} \PY{p}{=} 1\PY{p}{:}\PY{n+nb}{size}\PY{p}{(}\PY{n}{files}\PY{p}{,}1\PY{p}{)}
        \PY{n}{Image} \PY{p}{=} \PY{n}{imread}\PY{p}{(}\PY{p}{[}\PY{l+s}{'}\PY{l+s}{juggle1/'}\PY{p}{,} \PY{n}{files}\PY{p}{(}\PY{n}{ii}\PY{p}{)}\PY{p}{.}\PY{n}{name}\PY{p}{]}\PY{p}{)}\PY{p}{;}
        \PY{n}{avgbg} \PY{p}{=} \PY{n}{avgbg} \PY{o}{+} \PY{n}{double}\PY{p}{(}\PY{n}{Image}\PY{p}{)}\PY{p}{;}    
    \PY{k}{end} 


    \PY{n}{avgbg} \PY{p}{=} \PY{n}{uint8}\PY{p}{(}  \PY{n}{avgbg} \PY{o}{/} \PY{n+nb}{size}\PY{p}{(}\PY{n}{files}\PY{p}{,}1\PY{p}{)}  \PY{p}{)}\PY{p}{;} 
\PY{k}{end}

\end{Verbatim}

The other part of background subtraction is that we need to preserve
colors of the balls, since we detect them by color later.

We start by defining threshold values for each colour channel.

\begin{Verbatim}[commandchars=\\\{\}]\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{function}\PY{+w}{ }[res] \PY{p}{=}\PY{+w}{ }\PY{n+nf}{bgdiff}\PY{p}{(}m, bg\PY{p}{)}
\PY{+w}{    }\PY{n}{m} \PY{p}{=} \PY{n}{double}\PY{p}{(}\PY{n}{m}\PY{p}{)}\PY{p}{;}
    \PY{n}{bg} \PY{p}{=} \PY{n}{double}\PY{p}{(}\PY{n}{bg}\PY{p}{)}\PY{p}{;}

    \PY{n}{tred} \PY{p}{=} 20\PY{p}{;}
    \PY{n}{tgreen} \PY{p}{=} 10\PY{p}{;}
    \PY{n}{tblue} \PY{p}{=} 20\PY{p}{;} 
    \PY{n}{res} \PY{p}{=} \PY{n+nb}{zeros}\PY{p}{(}\PY{n+nb}{size}\PY{p}{(}\PY{n}{m}\PY{p}{)}\PY{p}{)}\PY{p}{;}


\end{Verbatim}

Then we loop through each pixel and compare the difference in colour of
our image and the background image to the threshold value. If the
difference is too big, we set the pixel to black, otherwise we keep the
original colour.

\begin{Verbatim}[commandchars=\\\{\}]    \PY{k}{for} \PY{n+nb}{i}\PY{p}{=}1\PY{p}{:}\PY{n+nb}{size}\PY{p}{(}\PY{n}{m}\PY{p}{,}1\PY{p}{)}
        \PY{k}{for} \PY{n+nb}{j}\PY{p}{=}1\PY{p}{:}\PY{n+nb}{size}\PY{p}{(}\PY{n}{m}\PY{p}{,}2\PY{p}{)}                    
            \PY{k}{if} \PY{n+nb}{abs}\PY{p}{(}\PY{n}{m}\PY{p}{(}\PY{n+nb}{i}\PY{p}{,}\PY{n+nb}{j}\PY{p}{,}1\PY{p}{)} \PY{o}{-} \PY{n}{bg}\PY{p}{(}\PY{n+nb}{i}\PY{p}{,}\PY{n+nb}{j}\PY{p}{,}1\PY{p}{)}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{n}{tred} \PY{o}{|} \PY{p}{.}\PY{p}{.}\PY{p}{.}
                    \PY{n+nb}{abs}\PY{p}{(}\PY{n}{m}\PY{p}{(}\PY{n+nb}{i}\PY{p}{,}\PY{n+nb}{j}\PY{p}{,}2\PY{p}{)} \PY{o}{-} \PY{n}{bg}\PY{p}{(}\PY{n+nb}{i}\PY{p}{,}\PY{n+nb}{j}\PY{p}{,}2\PY{p}{)}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{n}{tgreen} \PY{o}{|} \PY{p}{.}\PY{p}{.}\PY{p}{.}
                    \PY{n+nb}{abs}\PY{p}{(}\PY{n}{m}\PY{p}{(}\PY{n+nb}{i}\PY{p}{,}\PY{n+nb}{j}\PY{p}{,}3\PY{p}{)} \PY{o}{-} \PY{n}{bg}\PY{p}{(}\PY{n+nb}{i}\PY{p}{,}\PY{n+nb}{j}\PY{p}{,}3\PY{p}{)}\PY{p}{)} \PY{o}{\PYZgt{}} \PY{n}{tblue}
                \PY{n}{res}\PY{p}{(}\PY{n+nb}{i}\PY{p}{,}\PY{n+nb}{j}\PY{p}{,}\PY{p}{:}\PY{p}{)} \PY{p}{=} \PY{n}{m}\PY{p}{(}\PY{n+nb}{i}\PY{p}{,}\PY{n+nb}{j}\PY{p}{,} \PY{p}{:}\PY{p}{)}\PY{p}{;}
            \PY{k}{else}
                \PY{n}{res}\PY{p}{(}\PY{n+nb}{i}\PY{p}{,}\PY{n+nb}{j}\PY{p}{,}\PY{p}{:}\PY{p}{)} \PY{p}{=}  \PY{p}{[}0\PY{p}{;} 0\PY{p}{;} 0\PY{p}{]}\PY{p}{;}
            \PY{k}{end}        
        \PY{k}{end}
    \PY{k}{end}        


\end{Verbatim}

Since the difference is calculated from an average image, there are
plenty of artifacts that can confuse the later algorithm. We make a copy
of our image and threshold it to black and white. Then we erode the
images and use the result as a mask to further get rid of areas with
colours.

\begin{Verbatim}[commandchars=\\\{\}]    \PY{n}{res} \PY{p}{=} \PY{n}{uint8}\PY{p}{(}\PY{n}{res}\PY{p}{)}\PY{p}{;}          
    \PY{n}{n} \PY{p}{=} \PY{n}{bwmorph}\PY{p}{(}\PY{n}{im2bw}\PY{p}{(}\PY{n}{res}\PY{p}{,}0\PY{p}{.}15\PY{p}{)}\PY{p}{,} \PY{l+s}{'}\PY{l+s}{erode'}\PY{p}{,} 1\PY{p}{)}\PY{p}{;}

    \PY{n}{res} \PY{p}{=} \PY{n}{uint8}\PY{p}{(}\PY{n}{double}\PY{p}{(}\PY{n}{res}\PY{p}{)} \PY{o}{.*} \PY{n+nb}{repmat}\PY{p}{(}\PY{n}{n}\PY{p}{,} \PY{p}{[}1 1 3\PY{p}{]}\PY{p}{)}\PY{p}{)}\PY{p}{;}
\PY{k}{end}

\end{Verbatim}

Finally we need to identify the balls, for that we convert the color
into HSV colorspace and threshold on the hue. We've measured average
hues of the balls and chosen constants to pick them out.

Then we simply take the biggest blob from our image and find it's
centroid.

\begin{Verbatim}[commandchars=\\\{\}]\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{function}\PY{+w}{ }[C] \PY{p}{=}\PY{+w}{ }\PY{n+nf}{biggest\PYZus{}center}\PY{p}{(}BW\PY{p}{)}

\end{Verbatim}

Find the centroid of the biggest object

\begin{Verbatim}[commandchars=\\\{\}]    \PY{n}{CC} \PY{p}{=} \PY{n}{bwconncomp}\PY{p}{(}\PY{n}{BW}\PY{p}{)}\PY{p}{;}
    \PY{n}{S} \PY{p}{=} \PY{n}{regionprops}\PY{p}{(}\PY{n}{CC}\PY{p}{,}\PY{l+s}{'}\PY{l+s}{Centroid'}\PY{p}{)}\PY{p}{;}
    \PY{n}{numPixels} \PY{p}{=} \PY{n}{cellfun}\PY{p}{(}\PY{p}{@}\PY{n+nb}{numel}\PY{p}{,}\PY{n}{CC}\PY{p}{.}\PY{n}{PixelIdxList}\PY{p}{)}\PY{p}{;}
    \PY{p}{[}\PY{n}{biggest}\PY{p}{,}\PY{n}{idx}\PY{p}{]} \PY{p}{=} \PY{n}{max}\PY{p}{(}\PY{n}{numPixels}\PY{p}{)}\PY{p}{;}
    \PY{n}{C} \PY{p}{=} \PY{n}{S}\PY{p}{(}\PY{n}{idx}\PY{p}{)}\PY{p}{.}\PY{n}{Centroid}\PY{p}{;}
\PY{k}{end}

\end{Verbatim}

This alone turns out to work remarkably well (see below), however to
improve performance further, we decided to use our tracking information.
One constraint on the domain seems to be that the balls only travel a
certain distance in one time step. We measured what that is. Because
this is the case, we only want to look in the region of the image which
is a certain distance away from the last position. We decided to set
this area to 3 standard deviations of the mean of the distances between
successive frames of the true data set (the complete data set fits
within 2.5 standard deviation).

This allows us to get rid of some complete misclassifications like
detecting the reflection of the ball in the window.

\section{Performance}

To evaluate performance two metrics are used. Firstly we count the
number of misclassifications, which we define as any detection that is
more then 10 pixels away from the true data set. Secondly, we track the
average (euclidian) distance from the true data set.

The full system achieves 99.327\% within 10px of true center (97.980\%
for the red ball, 100.000\% for the yellow ball, 100.000\% for the blue
ball). Average distance from true center was 1.836px (SD=1.830).

The system without the tracking system is slightly worse, but still
achieves 97.306\% within 10 pixels of true center and in average is
5.975 pixels (SD=36.486799) from the true center.

\section{Example images}

\section{Discussion}

One of the problems with using an average image is that if the system
should be used as an online system, finding the balls in the first
couple of images can be quite difficult. As a simulation of how this
behaves we start with the basic background image and as more images come
in we iteratively improve our background image. This makes the first
roughly five images quite off, but converges quite quickly to fairly
smooth detection.

Iteratively we grow the store variable with all the images we have seen.
Store gets initiated to: store = zeros(width, height, 3, 0); Then we
apply this function with every image we see.

\begin{Verbatim}[commandchars=\\\{\}]\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{function}\PY{+w}{ }[store, bg] \PY{p}{=}\PY{+w}{ }\PY{n+nf}{avg\PYZus{}adaptive}\PY{p}{(}store, curr\PY{p}{)}
\PY{+w}{    }\PY{n}{store}\PY{p}{(}\PY{p}{:}\PY{p}{,} \PY{p}{:}\PY{p}{,} \PY{p}{:}\PY{p}{,} \PY{n+nb}{size}\PY{p}{(}\PY{n}{store}\PY{p}{,} 4\PY{p}{)} \PY{o}{+} 1\PY{p}{)} \PY{p}{=} \PY{n}{double}\PY{p}{(}\PY{n}{curr}\PY{p}{)}\PY{p}{;}
    \PY{n}{bg} \PY{p}{=} \PY{n+nb}{zeros}\PY{p}{(}\PY{n+nb}{size}\PY{p}{(}\PY{n}{store}\PY{p}{,} 1\PY{p}{)}\PY{p}{,} \PY{n+nb}{size}\PY{p}{(}\PY{n}{store}\PY{p}{,} 2\PY{p}{)}\PY{p}{,} 3\PY{p}{)}\PY{p}{;}

    \PY{k}{for} \PY{n+nb}{i} \PY{p}{=} 1\PY{p}{:}\PY{n+nb}{size}\PY{p}{(}\PY{n}{store}\PY{p}{,} 4\PY{p}{)}
       \PY{n}{bg} \PY{p}{=} \PY{n}{bg} \PY{o}{+} \PY{n}{double}\PY{p}{(}\PY{n}{store}\PY{p}{(}\PY{p}{:}\PY{p}{,} \PY{p}{:}\PY{p}{,} \PY{p}{:}\PY{p}{,} \PY{n+nb}{i}\PY{p}{)}\PY{p}{)}\PY{p}{;}
    \PY{k}{end}
    \PY{n}{bg} \PY{p}{=} \PY{n}{uint8}\PY{p}{(}\PY{n+nb}{round}\PY{p}{(}\PY{n}{bg} \PY{o}{./} \PY{n+nb}{size}\PY{p}{(}\PY{n}{store}\PY{p}{,} 4\PY{p}{)}\PY{p}{)}\PY{p}{)}\PY{p}{;}
\PY{k}{end}

\end{Verbatim}

The results we get from doing this online decrease to 88.215\% of
detected balls within 10px of true center.

\section{Appendix: Remaining Source Code}

\subsection{Task 1: Detection}

The algorithm starts by calculating the average background from all the
images gathered (see \texttt{avgall} bellow), and doing some setup. Also
an option for skipping this step is presented.

\begin{Verbatim}[commandchars=\\\{\}]\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{function}\PY{+w}{ }\PY{n+nf}{main}\PY{p}{(}skip\PYZus{}detection\PY{p}{)}\PY{+w}{    }
\PY{+w}{    }\PY{n}{avgbg} \PY{p}{=} \PY{n}{avgall}\PY{p}{;}

    \PY{n}{fg} \PY{p}{=} \PY{n}{figure}\PY{p}{(}1\PY{p}{)}\PY{p}{;}
    \PY{n}{files} \PY{p}{=} \PY{n}{dir}\PY{p}{(}\PY{l+s}{'}\PY{l+s}{juggle1/0*.jpg'}\PY{p}{)}\PY{p}{;}
    \PY{n}{tracks} \PY{p}{=} \PY{n+nb}{zeros}\PY{p}{(}\PY{n+nb}{size}\PY{p}{(}\PY{n}{files}\PY{p}{,}1\PY{p}{)}\PY{p}{,} 6\PY{p}{)}\PY{p}{;}
    \PY{n}{wb} \PY{p}{=} \PY{n}{waitbar}\PY{p}{(}0\PY{p}{,} \PY{l+s}{'}\PY{l+s}{Initializing'}\PY{p}{)}\PY{p}{;}
    \PY{n}{count} \PY{p}{=} \PY{n+nb}{size}\PY{p}{(}\PY{n}{files}\PY{p}{,}1\PY{p}{)}\PY{p}{;}

    \PY{k}{if} \PY{n}{nargin} \PY{o}{==} 1 \PY{o}{\PYZam{}} \PY{n}{skip\PYZus{}detection}
        \PY{n}{tracks} \PY{p}{=} \PY{n}{load}\PY{p}{(}\PY{l+s}{'}\PY{l+s}{track.mat'}\PY{p}{)}\PY{p}{;}
        \PY{n}{tracks} \PY{p}{=} \PY{n}{tracks}\PY{p}{.}\PY{n}{tracks}\PY{p}{;}
    \PY{k}{else}
        \PY{k}{for} \PY{n}{ii} \PY{p}{=} 1\PY{p}{:}\PY{n}{count}
            \PY{n}{tic}\PY{p}{;}
            \PY{n}{Image} \PY{p}{=} \PY{n}{imread}\PY{p}{(}\PY{p}{[}\PY{l+s}{'}\PY{l+s}{juggle1/'}\PY{p}{,} \PY{n}{files}\PY{p}{(}\PY{n}{ii}\PY{p}{)}\PY{p}{.}\PY{n}{name}\PY{p}{]}\PY{p}{)}\PY{p}{;}

\end{Verbatim}

The algorithm processes each input image. It substracts the average
background image, keeping the colours intact in places where the
difference is large enough. Then we calculate thresholds for the
individual color values.

\begin{Verbatim}[commandchars=\\\{\}]            \PY{n}{diff} \PY{p}{=} \PY{n}{bgdiff}\PY{p}{(}\PY{n}{Image}\PY{p}{,} \PY{n}{avgbg}\PY{p}{)}\PY{p}{;}

            \PY{n}{Y} \PY{p}{=} \PY{n}{thresh\PYZus{}yellow}\PY{p}{(}\PY{n}{diff}\PY{p}{)}\PY{p}{;}
            \PY{n}{B} \PY{p}{=} \PY{n}{thresh\PYZus{}blue}\PY{p}{(}\PY{n}{diff}\PY{p}{)}\PY{p}{;}
            \PY{n}{R} \PY{p}{=} \PY{n}{thresh\PYZus{}red}\PY{p}{(}\PY{n}{diff}\PY{p}{)}\PY{p}{;}


\end{Verbatim}

Then we calculate the centroid of the biggest continous blob in our
thresholded image and store them in our tracking matrix.

\begin{Verbatim}[commandchars=\\\{\}]            \PY{n}{cy} \PY{p}{=} \PY{n}{biggest\PYZus{}center}\PY{p}{(}\PY{n}{Y}\PY{p}{)}\PY{p}{;}
            \PY{n}{cb} \PY{p}{=} \PY{n}{biggest\PYZus{}center}\PY{p}{(}\PY{n}{B}\PY{p}{)}\PY{p}{;}
            \PY{n}{cr} \PY{p}{=} \PY{n}{biggest\PYZus{}center}\PY{p}{(}\PY{n}{R}\PY{p}{)}\PY{p}{;}
            \PY{n}{tracks}\PY{p}{(}\PY{n}{ii}\PY{p}{,} \PY{p}{:}\PY{p}{)} \PY{p}{=} \PY{p}{[}\PY{n}{cy}\PY{p}{,} \PY{n}{cb}\PY{p}{,} \PY{n}{cr}\PY{p}{]}\PY{p}{;}

            \PY{n}{set}\PY{p}{(}\PY{n}{fg}\PY{p}{,} \PY{l+s}{'}\PY{l+s}{name'}\PY{p}{,} \PY{n}{files}\PY{p}{(}\PY{n}{ii}\PY{p}{)}\PY{p}{.}\PY{n}{name}\PY{p}{)}\PY{p}{;}
            \PY{n}{imshow}\PY{p}{(}\PY{n}{R} \PY{o}{+} \PY{n}{Y} \PY{o}{+} \PY{n}{B}\PY{p}{)}\PY{p}{;}
            \PY{n}{hold} \PY{n}{on}
            \PY{n}{plot}\PY{p}{(}\PY{n}{cy}\PY{p}{(}1\PY{p}{)}\PY{p}{,} \PY{n}{cy}\PY{p}{(}2\PY{p}{)}\PY{p}{,} \PY{l+s}{'}\PY{l+s}{y*'}\PY{p}{,} \PY{n}{cb}\PY{p}{(}1\PY{p}{)}\PY{p}{,} \PY{n}{cb}\PY{p}{(}2\PY{p}{)}\PY{p}{,} \PY{l+s}{'}\PY{l+s}{b*'}\PY{p}{,} \PY{n}{cr}\PY{p}{(}1\PY{p}{)}\PY{p}{,} \PY{n}{cr}\PY{p}{(}2\PY{p}{)}\PY{p}{,} \PY{l+s}{'}\PY{l+s}{r*'}\PY{p}{)}\PY{p}{;}
            \PY{n}{drawnow}\PY{p}{;}
            \PY{n}{pause}\PY{p}{(}1 \PY{o}{-} \PY{n}{toc}\PY{p}{)}
            \PY{n}{perc} \PY{p}{=} \PY{n}{ii}\PY{o}{/}\PY{p}{(}\PY{n+nb}{size}\PY{p}{(}\PY{n}{files}\PY{p}{,}1\PY{p}{)} \PY{o}{*} 2 \PY{o}{+} 4\PY{p}{)}\PY{p}{;}
            \PY{n}{waitbar}\PY{p}{(}\PY{n}{perc}\PY{p}{,}\PY{n}{wb}\PY{p}{,}\PY{n}{sprintf}\PY{p}{(}\PY{l+s}{'}\PY{l+s}{\PYZpc{}d\PYZpc{}\PYZpc{} completed...'}\PY{p}{,}\PY{n+nb}{round}\PY{p}{(}\PY{n}{perc} \PY{o}{*} 100\PY{p}{)}\PY{p}{)}\PY{p}{)}\PY{p}{;}
        \PY{k}{end} 
        \PY{n}{save}\PY{p}{(}\PY{l+s}{'}\PY{l+s}{track.mat'}\PY{p}{,} \PY{l+s}{'}\PY{l+s}{tracks'}\PY{p}{)}\PY{p}{;}
    \PY{k}{end}


\end{Verbatim}

\subsection{Task 2: Tracking}

Tracking is largely done in the previous step, here we visualise the
individual required images as well as an overall image of the juggling.

\begin{Verbatim}[commandchars=\\\{\}]    \PY{n}{figure}\PY{p}{(}1\PY{p}{)}\PY{p}{;}
    \PY{n}{imshow}\PY{p}{(}\PY{n}{imread}\PY{p}{(}\PY{l+s}{'}\PY{l+s}{background.jpg'}\PY{p}{)}\PY{p}{)}
    \PY{n}{hold} \PY{n}{on}
    \PY{n}{plot}\PY{p}{(}\PY{n}{tracks}\PY{p}{(}\PY{p}{:}\PY{p}{,} 1\PY{p}{)}\PY{p}{,} \PY{n}{tracks}\PY{p}{(}\PY{p}{:}\PY{p}{,} 2\PY{p}{)}\PY{p}{,} \PY{l+s}{'}\PY{l+s}{y'}\PY{p}{,} \PY{n}{tracks}\PY{p}{(}\PY{p}{:}\PY{p}{,} 3\PY{p}{)}\PY{p}{,} \PY{p}{.}\PY{p}{.}\PY{p}{.}
        \PY{n}{tracks}\PY{p}{(}\PY{p}{:}\PY{p}{,} 4\PY{p}{)}\PY{p}{,} \PY{l+s}{'}\PY{l+s}{b'}\PY{p}{,} \PY{n}{tracks}\PY{p}{(}\PY{p}{:}\PY{p}{,} 5\PY{p}{)}\PY{p}{,} \PY{n}{tracks}\PY{p}{(}\PY{p}{:}\PY{p}{,} 6\PY{p}{)}\PY{p}{,} \PY{l+s}{'}\PY{l+s}{r'}\PY{p}{)}
    \PY{n}{print}\PY{p}{(}\PY{l+s}{'}\PY{l+s}{-dpng'}\PY{p}{,} \PY{l+s}{'}\PY{l+s}{report/tracking'}\PY{p}{)}

    \PY{n}{figure}\PY{p}{(}1\PY{p}{)}\PY{p}{;}
    \PY{n}{imshow}\PY{p}{(}\PY{n}{imread}\PY{p}{(}\PY{l+s}{'}\PY{l+s}{background.jpg'}\PY{p}{)}\PY{p}{)}
    \PY{n}{hold} \PY{n}{on}
    \PY{n}{plot}\PY{p}{(}\PY{n}{tracks}\PY{p}{(}\PY{p}{:}\PY{p}{,} 1\PY{p}{)}\PY{p}{,} \PY{n}{tracks}\PY{p}{(}\PY{p}{:}\PY{p}{,} 2\PY{p}{)}\PY{p}{,} \PY{l+s}{'}\PY{l+s}{y'}\PY{p}{)}
    \PY{n}{print}\PY{p}{(}\PY{l+s}{'}\PY{l+s}{-dpng'}\PY{p}{,} \PY{l+s}{'}\PY{l+s}{report/tracking-yellow'}\PY{p}{)}

    \PY{n}{figure}\PY{p}{(}1\PY{p}{)}\PY{p}{;}
    \PY{n}{imshow}\PY{p}{(}\PY{n}{imread}\PY{p}{(}\PY{l+s}{'}\PY{l+s}{background.jpg'}\PY{p}{)}\PY{p}{)}
    \PY{n}{hold} \PY{n}{on}
    \PY{n}{plot}\PY{p}{(}\PY{n}{tracks}\PY{p}{(}\PY{p}{:}\PY{p}{,} 3\PY{p}{)}\PY{p}{,} \PY{n}{tracks}\PY{p}{(}\PY{p}{:}\PY{p}{,} 4\PY{p}{)}\PY{p}{,} \PY{l+s}{'}\PY{l+s}{b'}\PY{p}{)}
    \PY{n}{print}\PY{p}{(}\PY{l+s}{'}\PY{l+s}{-dpng'}\PY{p}{,} \PY{l+s}{'}\PY{l+s}{report/tracking-blue'}\PY{p}{)}

    \PY{n}{figure}\PY{p}{(}1\PY{p}{)}\PY{p}{;}
    \PY{n}{imshow}\PY{p}{(}\PY{n}{imread}\PY{p}{(}\PY{l+s}{'}\PY{l+s}{background.jpg'}\PY{p}{)}\PY{p}{)}
    \PY{n}{hold} \PY{n}{on}
    \PY{n}{plot}\PY{p}{(}\PY{n}{tracks}\PY{p}{(}\PY{p}{:}\PY{p}{,} 5\PY{p}{)}\PY{p}{,} \PY{n}{tracks}\PY{p}{(}\PY{p}{:}\PY{p}{,} 6\PY{p}{)}\PY{p}{,} \PY{l+s}{'}\PY{l+s}{r'}\PY{p}{)}
    \PY{n}{print}\PY{p}{(}\PY{l+s}{'}\PY{l+s}{-dpng'}\PY{p}{,} \PY{l+s}{'}\PY{l+s}{report/tracking-red'}\PY{p}{)}



\end{Verbatim}

\subsection{Task 3: Evaluation}

We load the true data and calculate euclidian distance from the true
data and our tracked data. We then count the number of images that were
tracked more then 10px off as well as the average error.

\begin{Verbatim}[commandchars=\\\{\}]    \PY{n}{ev} \PY{p}{=} \PY{n}{load}\PY{p}{(}\PY{l+s}{'}\PY{l+s}{gt1.mat'}\PY{p}{)}\PY{p}{;}
    \PY{n}{gt} \PY{p}{=} \PY{n}{ev}\PY{p}{.}\PY{n}{gt1}\PY{o}{'}\PY{p}{;}

    \PY{n}{yellow\PYZus{}d} \PY{p}{=} \PY{n+nb}{sqrt}\PY{p}{(}\PY{n}{sum}\PY{p}{(}\PY{n}{gt}\PY{p}{(}\PY{p}{:}\PY{p}{,}\PY{p}{[}7\PY{p}{,}6\PY{p}{]}\PY{p}{)} \PY{o}{-} \PY{n}{tracks}\PY{p}{(}\PY{p}{:}\PY{p}{,}\PY{p}{[}1\PY{p}{,}2\PY{p}{]}\PY{p}{)}\PY{p}{,} 2\PY{p}{)} \PY{o}{.\PYZca{}} 2\PY{p}{)}\PY{p}{;}
    \PY{n}{blue\PYZus{}d}   \PY{p}{=} \PY{n+nb}{sqrt}\PY{p}{(}\PY{n}{sum}\PY{p}{(}\PY{n}{gt}\PY{p}{(}\PY{p}{:}\PY{p}{,}\PY{p}{[}5\PY{p}{,}4\PY{p}{]}\PY{p}{)} \PY{o}{-} \PY{n}{tracks}\PY{p}{(}\PY{p}{:}\PY{p}{,}\PY{p}{[}3\PY{p}{,}4\PY{p}{]}\PY{p}{)}\PY{p}{,} 2\PY{p}{)} \PY{o}{.\PYZca{}} 2\PY{p}{)}\PY{p}{;}
    \PY{n}{red\PYZus{}d}    \PY{p}{=} \PY{n+nb}{sqrt}\PY{p}{(}\PY{n}{sum}\PY{p}{(}\PY{n}{gt}\PY{p}{(}\PY{p}{:}\PY{p}{,}\PY{p}{[}3\PY{p}{,}2\PY{p}{]}\PY{p}{)} \PY{o}{-} \PY{n}{tracks}\PY{p}{(}\PY{p}{:}\PY{p}{,}\PY{p}{[}5\PY{p}{,}6\PY{p}{]}\PY{p}{)}\PY{p}{,} 2\PY{p}{)} \PY{o}{.\PYZca{}} 2\PY{p}{)}\PY{p}{;}

    \PY{n}{yellow\PYZus{}correct} \PY{p}{=} \PY{n}{sum}\PY{p}{(}\PY{n}{yellow\PYZus{}d} \PY{o}{\PYZlt{}} 10\PY{p}{)}\PY{p}{;}
    \PY{n}{blue\PYZus{}correct}   \PY{p}{=} \PY{n}{sum}\PY{p}{(}\PY{n}{blue\PYZus{}d} \PY{o}{\PYZlt{}} 10\PY{p}{)}\PY{p}{;}
    \PY{n}{red\PYZus{}correct}    \PY{p}{=} \PY{n}{sum}\PY{p}{(}\PY{n}{red\PYZus{}d} \PY{o}{\PYZlt{}} 10\PY{p}{)}\PY{p}{;}

    \PY{n}{overall\PYZus{}d} \PY{p}{=} \PY{p}{[}\PY{n}{yellow\PYZus{}d}\PY{p}{;} \PY{n}{blue\PYZus{}d}\PY{p}{;} \PY{n}{red\PYZus{}d}\PY{p}{]}\PY{p}{;}
    \PY{n}{overall}   \PY{p}{=} \PY{p}{(}\PY{n}{yellow\PYZus{}correct} \PY{o}{+} \PY{n}{blue\PYZus{}correct} \PY{o}{+} \PY{n}{red\PYZus{}correct}\PY{p}{)} \PY{o}{/} \PY{p}{(}\PY{n}{count} \PY{o}{*} 3\PY{p}{)}\PY{p}{;}

    \PY{n+nb}{disp}\PY{p}{(}\PY{n}{sprintf}\PY{p}{(}\PY{l+s}{'}\PY{l+s}{\PYZpc{}f\PYZpc{}\PYZpc{} within 10px of true center (R=\PYZpc{}f\PYZpc{}\PYZpc{}, Y=\PYZpc{}f\PYZpc{}\PYZpc{}, B=\PYZpc{}f\PYZpc{}\PYZpc{})'}\PY{p}{,} \PY{p}{.}\PY{p}{.}\PY{p}{.}
        \PY{n}{overall} \PY{o}{*} 100\PY{p}{,} \PY{n}{red\PYZus{}correct} \PY{o}{/} \PY{n}{count} \PY{o}{*} 100\PY{p}{,} \PY{n}{yellow\PYZus{}correct} \PY{o}{/} \PY{n}{count} \PY{o}{*} 100\PY{p}{,} \PY{p}{.}\PY{p}{.}\PY{p}{.}
        \PY{n}{blue\PYZus{}correct} \PY{o}{/} \PY{n}{count} \PY{o}{*} 100\PY{p}{)}\PY{p}{)}\PY{p}{;} 

    \PY{n+nb}{disp}\PY{p}{(}\PY{n}{sprintf}\PY{p}{(}\PY{l+s}{'}\PY{l+s}{Average distance from true center \PYZpc{}fpx (SD=\PYZpc{}f)'}\PY{p}{,} \PY{p}{.}\PY{p}{.}\PY{p}{.}
        \PY{n}{mean}\PY{p}{(}\PY{n}{overall\PYZus{}d}\PY{p}{)}\PY{p}{,} \PY{n}{std}\PY{p}{(}\PY{n}{overall\PYZus{}d}\PY{p}{)}\PY{p}{)}\PY{p}{)}\PY{p}{;}

    \PY{n}{fg} \PY{p}{=} \PY{n}{figure}\PY{p}{(}1\PY{p}{)}\PY{p}{;}
    \PY{n}{delete}\PY{p}{(}\PY{l+s}{'}\PY{l+s}{fixme/*.png'}\PY{p}{)}\PY{p}{;}

\end{Verbatim}

Finally we will display each image with the tracked center and the real
center, saving to disk those that are more then 10px off.

\begin{Verbatim}[commandchars=\\\{\}]    \PY{k}{for} \PY{n}{ii} \PY{p}{=} 1\PY{p}{:}\PY{n}{count}
        \PY{n}{tic}\PY{p}{;}
        \PY{n}{Image} \PY{p}{=} \PY{n}{imread}\PY{p}{(}\PY{p}{[}\PY{l+s}{'}\PY{l+s}{juggle1/'}\PY{p}{,} \PY{n}{files}\PY{p}{(}\PY{n}{ii}\PY{p}{)}\PY{p}{.}\PY{n}{name}\PY{p}{]}\PY{p}{)}\PY{p}{;}
        \PY{n}{set}\PY{p}{(}\PY{n}{fg}\PY{p}{,} \PY{l+s}{'}\PY{l+s}{name'}\PY{p}{,} \PY{n}{files}\PY{p}{(}\PY{n}{ii}\PY{p}{)}\PY{p}{.}\PY{n}{name}\PY{p}{)}\PY{p}{;}
        \PY{n}{imshow}\PY{p}{(}\PY{n}{Image}\PY{p}{)}\PY{p}{;}
        \PY{n}{hold} \PY{n}{on}
        \PY{n}{plot}\PY{p}{(}\PY{n}{tracks}\PY{p}{(}\PY{n}{ii}\PY{p}{,} 1\PY{p}{)}\PY{p}{,} \PY{n}{tracks}\PY{p}{(}\PY{n}{ii}\PY{p}{,} 2\PY{p}{)}\PY{p}{,} \PY{l+s}{'}\PY{l+s}{y+'}\PY{p}{,} \PY{p}{.}\PY{p}{.}\PY{p}{.}
            \PY{n}{tracks}\PY{p}{(}\PY{n}{ii}\PY{p}{,} 3\PY{p}{)}\PY{p}{,} \PY{n}{tracks}\PY{p}{(}\PY{n}{ii}\PY{p}{,} 4\PY{p}{)}\PY{p}{,} \PY{l+s}{'}\PY{l+s}{b+'}\PY{p}{,} \PY{p}{.}\PY{p}{.}\PY{p}{.}
            \PY{n}{tracks}\PY{p}{(}\PY{n}{ii}\PY{p}{,}5\PY{p}{)}\PY{p}{,} \PY{n}{tracks}\PY{p}{(}\PY{n}{ii}\PY{p}{,} 6\PY{p}{)}\PY{p}{,} \PY{l+s}{'}\PY{l+s}{r+'}\PY{p}{)}\PY{p}{;}
        \PY{n}{plot}\PY{p}{(}\PY{n}{gt}\PY{p}{(}\PY{n}{ii}\PY{p}{,} 7\PY{p}{)}\PY{p}{,} \PY{n}{gt}\PY{p}{(}\PY{n}{ii}\PY{p}{,} 6\PY{p}{)}\PY{p}{,} \PY{l+s}{'}\PY{l+s}{y*'}\PY{p}{,} \PY{p}{.}\PY{p}{.}\PY{p}{.}
            \PY{n}{gt}\PY{p}{(}\PY{n}{ii}\PY{p}{,}5\PY{p}{)}\PY{p}{,} \PY{n}{gt}\PY{p}{(}\PY{n}{ii}\PY{p}{,} 4\PY{p}{)}\PY{p}{,} \PY{l+s}{'}\PY{l+s}{b*'}\PY{p}{,} \PY{p}{.}\PY{p}{.}\PY{p}{.}
            \PY{n}{gt}\PY{p}{(}\PY{n}{ii}\PY{p}{,}3\PY{p}{)}\PY{p}{,} \PY{n}{gt}\PY{p}{(}\PY{n}{ii}\PY{p}{,}2\PY{p}{)}\PY{p}{,} \PY{l+s}{'}\PY{l+s}{r*'}\PY{p}{)}\PY{p}{;}
        \PY{n}{drawnow}\PY{p}{;}
        \PY{n}{pause}\PY{p}{(}1 \PY{o}{-} \PY{n}{toc}\PY{p}{)}
        \PY{n}{perc} \PY{p}{=} \PY{p}{(}\PY{n}{ii} \PY{o}{+} \PY{n+nb}{size}\PY{p}{(}\PY{n}{files}\PY{p}{,}1\PY{p}{)}\PY{p}{)}\PY{o}{/}\PY{p}{(}\PY{n+nb}{size}\PY{p}{(}\PY{n}{files}\PY{p}{,}1\PY{p}{)} \PY{o}{*} 2 \PY{o}{+} 4\PY{p}{)}\PY{p}{;}

        \PY{p}{[}\PY{n}{pathstr}\PY{p}{,} \PY{n}{name}\PY{p}{,} \PY{n}{ext}\PY{p}{]} \PY{p}{=} \PY{n}{fileparts}\PY{p}{(}\PY{n}{files}\PY{p}{(}\PY{n}{ii}\PY{p}{)}\PY{p}{.}\PY{n}{name}\PY{p}{)}\PY{p}{;}

        \PY{k}{if} \PY{n}{yellow\PYZus{}d}\PY{p}{(}\PY{n}{ii}\PY{p}{)} \PY{o}{\PYZgt{}} 10 
            \PY{n}{print}\PY{p}{(}\PY{l+s}{'}\PY{l+s}{-dpng'}\PY{p}{,} \PY{p}{[}\PY{l+s}{'}\PY{l+s}{fixme/'} \PY{n}{name} \PY{l+s}{'}\PY{l+s}{yellow'}\PY{p}{]}\PY{p}{)}\PY{p}{;}
        \PY{k}{end}
        \PY{k}{if} \PY{n}{blue\PYZus{}d}\PY{p}{(}\PY{n}{ii}\PY{p}{)} \PY{o}{\PYZgt{}} 10
            \PY{n}{print}\PY{p}{(}\PY{l+s}{'}\PY{l+s}{-dpng'}\PY{p}{,} \PY{p}{[}\PY{l+s}{'}\PY{l+s}{fixme/'} \PY{n}{name} \PY{l+s}{'}\PY{l+s}{blue'}\PY{p}{]}\PY{p}{)}\PY{p}{;}
        \PY{k}{end}
        \PY{k}{if} \PY{n}{red\PYZus{}d}\PY{p}{(}\PY{n}{ii}\PY{p}{)} \PY{o}{\PYZgt{}} 10
            \PY{n}{print}\PY{p}{(}\PY{l+s}{'}\PY{l+s}{-dpng'}\PY{p}{,} \PY{p}{[}\PY{l+s}{'}\PY{l+s}{fixme/'} \PY{n}{name} \PY{l+s}{'}\PY{l+s}{red'}\PY{p}{]}\PY{p}{)}\PY{p}{;}
        \PY{k}{end}

        \PY{n}{waitbar}\PY{p}{(}\PY{n}{perc}\PY{p}{,}\PY{n}{wb}\PY{p}{,}\PY{n}{sprintf}\PY{p}{(}\PY{l+s}{'}\PY{l+s}{\PYZpc{}d\PYZpc{}\PYZpc{} completed...'}\PY{p}{,}\PY{n+nb}{round}\PY{p}{(}\PY{n}{perc} \PY{o}{*} 100\PY{p}{)}\PY{p}{)}\PY{p}{)}\PY{p}{;}
    \PY{k}{end} 

    \PY{n}{close}\PY{p}{(}\PY{n}{fg}\PY{p}{)}\PY{p}{;}
    \PY{n}{close}\PY{p}{(}\PY{n}{wb}\PY{p}{)}\PY{p}{;}

\PY{k}{end}

\end{Verbatim}

\subsection{Thresholding functions}

\begin{Verbatim}[commandchars=\\\{\}]\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{function}\PY{+w}{ }[res] \PY{p}{=}\PY{+w}{ }\PY{n+nf}{thresh\PYZus{}blue}\PY{p}{(}m\PY{p}{)}
\PY{+w}{  }\PY{n}{mhsv} \PY{p}{=} \PY{n+nb}{rgb2hsv}\PY{p}{(}\PY{n}{m}\PY{p}{)}\PY{p}{;}  
  \PY{n}{h} \PY{p}{=} \PY{n}{mhsv}\PY{p}{(}\PY{p}{:}\PY{p}{,}\PY{p}{:}\PY{p}{,}1\PY{p}{)}\PY{p}{;}
  \PY{n}{res} \PY{p}{=} \PY{n}{h} \PY{o}{\PYZgt{}} 0\PY{p}{.}47 \PY{o}{\PYZam{}} \PY{n}{h} \PY{o}{\PYZlt{}} 0\PY{p}{.}65\PY{p}{;}
\PY{k}{end}

\end{Verbatim}

\begin{Verbatim}[commandchars=\\\{\}]\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{function}\PY{+w}{ }[res] \PY{p}{=}\PY{+w}{ }\PY{n+nf}{thresh\PYZus{}yellow}\PY{p}{(}m\PY{p}{)}
\PY{+w}{  }\PY{n}{mhsv} \PY{p}{=} \PY{n+nb}{rgb2hsv}\PY{p}{(}\PY{n}{m}\PY{p}{)}\PY{p}{;}
  \PY{n}{h} \PY{p}{=} \PY{n}{mhsv}\PY{p}{(}\PY{p}{:}\PY{p}{,}\PY{p}{:}\PY{p}{,}1\PY{p}{)}\PY{p}{;}
  \PY{n}{res} \PY{p}{=} \PY{n}{h} \PY{o}{\PYZgt{}} 0\PY{p}{.}13 \PY{o}{\PYZam{}} \PY{n}{h} \PY{o}{\PYZlt{}} 0\PY{p}{.}25\PY{p}{;}
\PY{k}{end}

\end{Verbatim}

\begin{Verbatim}[commandchars=\\\{\}]\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{function}\PY{+w}{ }[res] \PY{p}{=}\PY{+w}{ }\PY{n+nf}{thresh\PYZus{}red}\PY{p}{(}m\PY{p}{)}
\PY{+w}{  }\PY{n}{mhsv} \PY{p}{=} \PY{n+nb}{rgb2hsv}\PY{p}{(}\PY{n}{m}\PY{p}{)}\PY{p}{;}  
  \PY{n}{h} \PY{p}{=} \PY{n}{mhsv}\PY{p}{(}\PY{p}{:}\PY{p}{,}\PY{p}{:}\PY{p}{,}1\PY{p}{)}\PY{p}{;}
  \PY{n}{res} \PY{p}{=} \PY{n}{h} \PY{o}{\PYZgt{}} 0\PY{p}{.}9\PY{p}{;}
\PY{k}{end}

\end{Verbatim}


\end{document}